The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
reflow hab class section

## Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at <!-- TODO:
double check lc res--> 10 m resolution. We reclassified the landcover types into
three categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat <!-- TODO: "foraging" should
be "lichen" ?--> consisted of lichen habitat, open habitat consisted of wetland,
rocky barrens, and anthropogenic habitat types, while forest habitat consisted
of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest
habitat types. Water habitat was excluded from all subsequent analyses.

>>>>

## Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at <!-- TODO:
double check lc res--> 10 m resolution. We reclassified the landcover types into
three categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broadleaf forest, and mixed-wood forest habitat types. Water habitat was
excluded from all subsequent analyses.
